IFA Comparison of Noncognitive Skills \\ BCS and MCS

### 2018-04-25 codes/R/paper/cohorts_nc.Rnw
add EFA in appendix

For ease of interpretation, I choose to rescale the factor loadings using \emph{oblimin} rotation: this method allows the underlying factors to be correlated to each other. From the results of the exploratory FA and IRT analysis with 2 factors, the pattern that seems to emerge is consistent with the theoretical constructs of externalising (EXT) and internalising (INT) behaviour problems.
% 
% <<BCSEFA>>=
% @
% 
% <<BCSEFARES, dependson='BCSEFA', echo=T, results='markup'>>=
% @

@@

% 
% <<MCSEFA>>=
% @
% 
% # <<MCSEFARES, dependson='BCSEFA', echo=T, results='markup'>>=
% # @
%

@@

\clearpage
\begin{appendices}
\section{Estimated model parameters}

>>>>

For ease of interpretation, I choose to rescale the factor loadings using \emph{oblimin} rotation: this method allows the underlying factors to be correlated to each other. From the results of the exploratory FA and IRT analysis with 2 factors, the pattern that seems to emerge is consistent with the theoretical constructs of externalising (EXT) and internalising (INT) behaviour problems.

@@

@@

\clearpage
\begin{appendices}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Exploratory Factor Analysis}

<<BCSEFA>>=
@

<<MCSEFA>>=
@

<<BCSEFARES, dependson='BCSEFA', results='markup'>>=
@

<<MCSEFARES, dependson='BCSEFA', results='markup'>>=
@

\begin{table}[ht]
\caption{Number of factors} \label{tab:nfac}
<<EFATAB, dependson='MCSEFARES', results='asis'>>=
# combine results
efatab <- cbind(efatab.bcs,efatab.mcs)
colnames(efatab) <- c("BCS All", "BCS M", "BCS F", "MCS All", "MCS M", "MCS F")

print(xtable(efatab,
                    align="L{.25\\textwidth}C{.08\\textwidth}C{.08\\textwidth}C{.08\\textwidth}C{.08\\textwidth}C{.08\\textwidth}C{.08\\textwidth}",
                    digits = 0
                    ), 
             size="\\small",
             include.rownames=T,
             include.colnames=T,
             booktabs = T,
             sanitize.text.function = function(x){x},
             tabular.environment = "tabular", width = ".8\\textwidth",
             floating = FALSE
)
@
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\section{Estimated model parameters}
